%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Arista Networks} % Organization
    {Santa Clara, CA} % Location
    {Jun. 2018 - Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented a new FPGA version look-up method which could reduce the reboot time of the switch by 1 minute}
        \item {Implemented the single event upset (SEU) recovery mechanism on FPGA to automate the detection and repairing of the CRC error without affecting the network traffic}
        \item {Enhanced the command line interface with the ability to display information about the software corrected CRC errors}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Engineering Intern} % Job title
    {ProductBio} % Organization
    {San Diego (remote), CA} % Location
    {Jan. 2018 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Structured and sanitized over ten thousands entries of raw merchandise data against the company's database schema using PostgreSQL}
        \item {Developed and validated a predictive model that explains the correlation between products' pricing and the environmental attributes}
        \item {Applied Principle component analysis(PCA) on the model for visualization}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Meitu} % Organization
    {Xiamen, China} % Location
    {Jun. 2017 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved the image conversion efficiency through integrating open source libraries into the company's image codecs project in C++}
        \item {Achieved 2x speedup over the core image filtering algorithms by refactoring code structures, applying matrix operations and using multi-threading}
        \item {Designed and implemented demos of 3D rendered images and animation with WebGL and ThreeJS}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Undergraduate Teaching Assistant} % Job title
    {UC San Diego} % Organization
    {La Jolla, CA} % Location
    {Jan. 2017 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Hosted office hours and graded assignments}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
